TAR System Description Paper Template

### 2017-05-29 paper/paper.tex
Added some text

\usepackage[utf8]{inputenc}
\usepackage[pdftex]{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{makecell}

@@

In this paper we will focus on the author diarization task proposed on PAN 2016 competition\footnote{\texttt{http://pan.webis.de/clef16/pan16-web/author-identification.html}}. The aim of this task is to decompose a document into its authorial parts, i.e. to split a text into segments and assign an author to every segment \citep{koppel-2011,aldebei-2015}. This is one of the unsupervised variants of authorship attribution problem since text samples of known authorship are not available \citep{rosso-2016}. As we will describe, in two out of three subtasks of this task only a correct number of authors for a given document is known.

@@

\section{The proposed approaches}
clustering, sliding window
pipeline: preprocessing (tokenization) -> basic features -> transformed features (including scaling) -> clustering

clustering metric

@@

\section{Experimantal results}

@@

>>>>

\usepackage[utf8]{inputenc}
\usepackage[pdftex]{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{makecell}
\usepackage[hyphens]{url}

@@

In this paper we will focus on the author diarization task proposed on PAN 2016 competition\footnote{\url{http://pan.webis.de/clef16/pan16-web/author-identification.html}}. The aim of this task is to decompose a document into its authorial parts, i.e. to split a text into segments and assign an author to every segment \citep{koppel-2011,aldebei-2015}. This is one of the unsupervised variants of authorship attribution problem since text samples of known authorship are not available \citep{rosso-2016}. As we will describe, in two out of three subtasks of this task only a correct number of authors for a given document is known.

@@

\section{Author Diarization?}
% describe the problem
% define formally: document, segmentation, segment, author assignement (label)
% define evaluation metrics

Let $D$ be the domain of documents. We define a document $d\in D$ as a finite sequence of tokens $t_i$, i.e. $d = (t_1, \dots, t_n)$ and $n$ can differ among documents.

For each document, there is a corresponding mapping to a sequence of labels $(a_1, \dots, a_n)$, that are representing groupings of tokens by authors. The labels $a_i$ are indices of authors of the document, and they range from $1$ to $m$, where $m$ is the number of authors of the document. Each token $t\in d$ is assigned a document-level label associating it to an author. Equivalently, the codomain of the mapping can also be defined as a set of segments $S$. A segment $s$ is a set of tokens where each is assigned the same label and the following applies:
\begin{equation}
	t_{i_1}\in s\ \wedge t_{i_2}\in s \wedge  i_1<i_3<i_2 \Rightarrow t_{i_3} \in s.
\end{equation}
Also, for a set of segments to be valid, the segments must cover all terms in the document and not overlap:
\begin{equation}
	\bigcup_{s\in S}s = T_d  \wedge \bigcap_{s\in S}s = \{\},
\end{equation}
where $T_d$ is the set of all terms in document $d$.

Let $\mathcal{D}$ be a

%\section{The proposed approach}
% clustering, sliding window
% pipeline: preprocessing (tokenization) -> basic features -> transformed features (including scaling) -> clustering
% define the pipeline formally P = (f_p: d\times->t, f_b: t->\phi, f_t: \phi->\phi', c: \phi'->labels, f_s: labels\times d->s)
% describe GroupRepel loss, describe AutoKMeans, 
% clustering metric

@@

\section{Experimental results}

@@

\section{Further work}
% more systematic parameter choice, model development
% mention possible applicability to author clustering and extrinsic plagiarism detections
